Performance of two different ontological and data access methods

### 2014-07-11 cold2014/magnus.tex
final spellcheck
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@755 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{abstract}
  We evaluate two different approaches that have been used in the
  literature and in practice by different groups publishing metadata
  about cars when consumed by a prototype application. These
  approaches are characterized by a generic vs. domain specific
  ontology; by a constrained tree-oriented API vs. openly queryable
  data; encouraging vs discouraging reasoning, etc.  We have
  implemented a prototype application where a potential user may query
  selected properties of cars, and we investigate how the different
  choices made by the original designers influence the performance of
  the application. For the evaluation, we employ the statistical
  discipline of Design of Experiments.

>>>>

\begin{abstract}
  We evaluate two different approaches that have been used in the
  literature and in practice by different groups publishing meta-data
  about cars when consumed by a prototype application. These
  approaches are characterized by a generic vs. domain specific
  ontology; by a constrained tree-oriented API vs. openly queryable
  data; encouraging vs discouraging reasoning, etc.  We have
  implemented a prototype application where a potential user may query
  selected properties of cars, and we investigate how the different
  choices made by the original designers influence the performance of
  the application. For the evaluation, we employ the statistical
  discipline of Design of Experiments.
